Analysis

### 2019-12-12 analysis.Rmd
ortografia

table_ed_gapper$ocup2 <- factor(table_ed_gapper$Educacion, levels=c(1,2,3,4), labels=c("Basica o menos", "Media completa", "Tecnico completa" , "Univercitario o más"))

@@

table_ed_gapjus$ocup2 <- factor(table_ed_gapjus$Educacion, levels=c(1,2,3,4), labels=c("Basica o menos", "Media completa", "Tecnico completa" , "Univercitario o más"))

>>>>

table_ed_gapper$ocup2 <- factor(table_ed_gapper$Educacion, levels=c(1,2,3,4), labels=c("Basica o menos", "Media completa", "Tecnico completa" , "Universitario o más"))

@@

table_ed_gapjus$ocup2 <- factor(table_ed_gapjus$Educacion, levels=c(1,2,3,4), labels=c("Basica o menos", "Media completa", "Tecnico completa" , "Universitario o más"))
